---
title: "Assignment 2"
author: "Averill Cate, Jr"
date: "February 23, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Assignment 2
## 1. What are the different data types supported by R?  
R's data types are vectors, arrays, data frames, lists, factors,  matrices, numeric, character and logical and integer.

Create a vector consisting of the first thousand numbers.
```{r}
v = 1L:1000L
tail(v, 10)
```
## 2. Using the control structures, write a program to

### a. find the odd numbers from the above created vector
I did this two ways.  
```{r}
# With control structures
find.odds <- function(values) {
  l = c(0)
  for(v in values) {
    if (values[[v]] %% 2 == 1) {
        l = c(l, values[[v]])
    }
  }
  return(l)
}
head(find.odds(v), 20)
tail(find.odds(v), 20)

# Without control structures
find.odds <- function(values) {
  result <- values[c(T,F)]
  return(result)
}
head(find.odds(v), 20)
tail(find.odds(v), 20)
```


### b. Find all the numbers divisible by 7.
I did this two ways.  
```{r}
# With control structures
divby.seven <- function(values) {
  l = c(0)
  for(v in values) {
    if (values[[v]] %% 7 == 0) {
        l = c(l, values[[v]])
    }
  }
  return(l)

}
head(divby.seven(v), 20)
tail(divby.seven(v), 20)

# Without control structures
divby.seven <- function(values) {
  indexes = values %% 7
  return(values[!indexes])
}
head(divby.seven(v), 20)
tail(divby.seven(v), 20)
```

## 3. Write a function in R which

### a. Takes an input of three sides and tells whether it is an equilateral triangle, isosceles or scalene triangle.
```{r}
triangle.type <- function(s1, s2, s3) {
  data = c(s1, s2, s3)
  fdata = factor(data)
  levs = nlevels(fdata)
  if ( levs == 2) {
    return("isoceles")
  } else if (levs == 1) {
    return("equilateral")
  } else {
    return("scalene")
  }
}

print(triangle.type(1,2,3))
print(triangle.type(2,2,3))
print(triangle.type(2,2,2))
print(triangle.type(4,1,2))
print(triangle.type(4,4,4))
```


### b. Takes two points (x,y) and finds the Cartesian distance between the 2D plane.
```{r}
cartesian.distance <- function(p1, p2) {
  dist = NULL
  t = (p2 - p1)^2
  s = sum(t)
  d = sqrt(s)
  return(d)
}
print(cartesian.distance(c(1,1), c(2,2)))
print(cartesian.distance(c(1,1), c(4,7)))
```