---
title: "Introduction to R - Assignment 2"
author: Averill Cate, Jr
date: Spring 2018
output:
  pdf_document: default
  html_notebook: default
---

# 1. For missouri.tract dataframe, print the first 30 rows of data.  
```{r}
library(UScensus2000tract)
library(dplyr)
```
# 2. Find the datatype of all the columns and comment about the N/A values in each column.  
```{r}
# Show the column types
data("missouri.tract")
mtd = missouri.tract@data
str(mtd)
```

```{r}
# Show some data
head(missouri.tract@data, 125)
```
Missing data could be due to many factors.  One reason could be an error in data entry, maybe an omission or incorrect data type was entered.  Also, this is cenuse/demographic data and geospatial data, so there may be no data points for certain geographic regions based on ethnicity.

# 3. Find the unique values for at least 5 columns of the above dataset
```{r}
# Data columns
mt = missouri.tract@data[4:9]
head(mt, 10)
# Unique values for all of the shosen data columns
mt_unique = lapply(mt, n_distinct)
mt_unique
```
